Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-06-13 paper/ms.tex
typo
segunda respuesta, modificacion en el cuerpo del paper

We chose this simulation based on three requirements. 
First, the simulation should have cosmological parameters consistent
with the most recent constraints from Cosmic Microwave Background
experiments and provide public acces to the data.
Second, the halo mass function from the simulation should be robust
down to masses that include the range of possibilities from previous
observational efforts \cite[e.g. results from][impose a lower bound of
  $10^{10}$\hMsun.]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16} .
Third, the total volume of the simulation should be at least 10 times
larger the equivalent volume of a single LAE observation field.
This conditions are met as we describe below.

@@

The preferred $1-\sigma$ range for the masses is $10.0<\log \mmin<11.2$
and $11.0<\log\mmax<13.0$.
\focc\ is completely determined by \mmin\ from \focc$=$0.011 when
$\log\mmin=10.0$ to $\focc=0.39$ when $\log\mmin=11.15$. 
We compute the power-law dependence between \focc\ and \mmin\ to be 
\begin{equation}
\focc = 0.08\left(\frac{\mmin}{10^{10.3}\hMsun}\right)^{0.77}.
\end{equation}
We remind the reader that models with $\log \focc>0.00$ ($\focc>1$)
correspond to cases where the halo number density is smaller 
than the number of observed LAEs but are  still considered consistent
because of the expected uncertainty in the median number density of
LAEs due to cosmic variance (see Fig. \ref{fig:cosmicv0} and
\S\ref{subsec:explore}).

>>>>

We chose this simulation based on three requirements. 
First, the simulation should have cosmological parameters consistent
with the most recent constraints from Cosmic Microwave Background
experiments and provide public acces to the data.
Second, the halo mass function from the simulation should be robust
down to masses that include the range of possibilities from previous
observational efforts \cite[e.g. results from][impose a lower bound of
  $10^{10}$\hMsun.]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16} .
Third, the total volume of the simulation should be at least 10 times
larger the equivalent volume of a single LAE observation field.
These conditions are met as we describe below.

@@

The preferred $1-\sigma$ range for the masses is $10.0<\log \mmin<11.2$
and $11.0<\log\mmax<13.0$.
\focc\ is completely determined by \mmin\ from \focc$=$0.011 when
$\log\mmin=10.0$ to $\focc=0.39$ when $\log\mmin=11.15$. 
We compute the power-law dependence between \focc\ and \mmin\ to be 
\begin{equation}
\focc = 0.08\left(\frac{\mmin}{10^{10.3}\hMsun}\right)^{0.77}.
\label{eq:focc}
\end{equation}
We remind the reader that models with $\log \focc>0.00$ ($\focc>1$)
correspond to cases where the halo number density is smaller 
than the number of observed LAEs but are  still considered consistent
because of the expected uncertainty in the median number density of
LAEs due to cosmic variance (see Fig. \ref{fig:cosmicv0} and
\S\ref{subsec:explore}).

The result in Eq.(\ref{eq:focc}) can be qualitatively understood as
follows.   
A choice of $\focc<1$ means that the halo mass function is scaled down.
If \mmin\ decreases the total number of halos increases because less
massive halos are more abundant.
This requires smaller values of $\focc$ to keep the total
number of halos equal to the number of LAES in observations.
